%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/rujhanarora/}{\Large Sam Dinshaw}} & Email : \href{mailto:sdinsh1@lsu.edu}{sdinsh1@lsu.edu}\\
  \href{https://www.linkedin.com/in/sam-dinshaw/}{{https://www.linkedin.com/in/sam-dinshaw/}} & Mobile : (504) 444-6551 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Louisiana State University A\&M (LSU), Baton Rouge}{Baton Rouge, Louisiana}
      {BS in Chemistry, BS in Physics;  GPA: 3.967}{Aug. 2024 -- Present}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart



        
    \resumeSubheading
        {LSU Department of Chemistry}{Baton Rouge, Louisiana}
        {Lopata Lab}{Jan. 2025 -- Present}
        \resumeItemListStart
        \resumeItem{Undergraduate Researcher}
            {Currently designing computational experiments using real-time time-dependent density functional theory by probing the electron density of UV-excited molecules and calculating their transient absorption spectra. }

        \resumeItemListEnd

    \resumeSubheading
        {LSU Department of Chemistry}{Baton Rouge, Louisiana}
        {Xu Lab}{Aug. 2024 -- Dec. 2024}
        \resumeItemListStart
        \resumeItem{Undergraduate Researcher}
            {Assisted with a project investigating the mechanisms behind the use of aluminum adjuvants in vaccines in order to increase vaccine efficacy. }

        \resumeItemListEnd

    \resumeSubheading
        {LSU HSC, Neuroscience Center of Excellence}{New Orleans, Louisiana}
        {Bazan Lab}{May 2023 -- Aug. 2023}
        \resumeItemListStart
        \resumeItem{Research Assistant}
            {Applied previous research experience to my interest in neuroscience and worked primarily in an analytical mass spectrometry lab; presented my research on sphingolipids to the neuroscience center in an oral presentation titled Ceramide and Sphingomyelin Abundance in RPE and Retina of ELOVL1 CKO; 8 weeks, 40 hours per week. }

        \resumeItemListEnd


    \resumeSubheading
        {UNO, Advanced Materials Research Institute}{New Orleans, Louisiana}
        {Rick Research Group}{May 2022 -- Aug. 2022}
        \resumeItemListStart
        \resumeItem{Research Assistant}
            {Utilized existing knowledge of Linux bash shell and chemistry for a research project in molecular dynamics/computational chemistry. Presented my research at an AMRI forum. Paper was later published in the Journal of Chemical Theory and Computation: Calculations of Absolute Free Energies, Enthalpies, and Entropies for Drug Binding; 8 weeks, 40 hours per week. }

        \resumeItemListEnd
        
    

  \resumeSubHeadingListEnd


%-----------TEACHING-----------------
\section{Teaching and Mentorship}
  \resumeSubHeadingListStart
    \resumeSubItem{Organic Chemistry SI Leader (Jan. 2026 – Present)}
      {\\Plans and facilitates biweekly review sessions with the intent of engaging students and helping them develop intuition and mastery of the content presented in the organic chemistry class. Hosts 2 office hours per week for more individual and personalized academic assistance.}
      
    \resumeSubItem{Math Circle Junior Group Leader (Jan. 2026 - Present)}
      {\\Facilitates group activities and other interactive experiences for local middle schoolers between 6th and 8th grade to help develop fundamental mathematical problem solving techniques, especially useful for competition math.}
    
    \resumeSubItem{Peer Mentor for SCI 1002 (Fall 2025)}
      {\\Facilitated and directed in-class discussions in SCI 1002, the College of Science's first-year course in preparing for a science major.}

    \resumeSubItem{Note Taker for BIOL1201 (Fall 2024)}
        {\\Worked with LSU Disability Services to assist peers registered with Disability Services by creating personalized notes.}
    
  \resumeSubHeadingListEnd

        

%-----------PROJECTS-----------------



\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubItem{LSU Cure Lab}
        {\\Participated in the honors section of the biology lab in which I had the opportunity to work on an original research project investigating the origin of parasitic behavior within the Taphrinomycotina through a phylogenetic analysis of ERG25 and other highly conserved genes. Spring 2025.}
    
    \resumeSubItem{LSU Cure Lab}
        {\\Participated in the honors section of the biology lab in which I had the opportunity to work on an original research project investigating the interaction of the Drosophila insulator protein BEAF-32 with select chromatin proteins involved in transcription regulation. Fall 2025.}
    \resumeSubItem{Documentation of Parsi Gujarati}
        {\\Creates wordlists and recordings of endangered Parsi-Gujarati dialect from native speakers (~70,000 Parsis remaining); collection will benefit Parsis community members without knowledge of Parsi-Gujarati (especially adolescent Parsis such as myself).}


  \resumeSubHeadingListEnd


%----------------PUBS_ACHIEVEMENTS---
\section{Achievements and Publications}
    \resumeSubHeadingListStart
        \resumeSubItem{Calculations of Absolute Free Energies, Enthalpies, and Entropies for Drug Binding}
            {\href{https://doi.org/10.1021/acs.jctc.4c00057}{{https://doi.org/10.1021/acs.jctc.4c00057//}}}

        \resumeSubItem{Global Ambassador}
        {\\Nominated by college dean to be the College of Science's representative for a week of interdisciplinary study in Dakar, Senegal.}

        \resumeSubItem{CURE Lab Poster Session Presenter}
        {\\Selected twice from among peers to present my original research projects at the CURE lab poster session.}

        \resumeSubItem{President's Alumni Scholarship}
        {\\Awarded to the top 21 freshman applicants to LSU alongside the Stamps Scholarship out of approximately 40,000 applications from the Class of 2028.}

    \resumeSubHeadingListEnd

    

%------------INVOLVEMENT--------------

\section{Involvement}
    \resumeSubHeadingListStart
        \resumeSubItem{Athletic Band and Concert Ensembles Member (Fall 2024 - Present)}
        {\\Tiger Band Member (Athletic Marching Band) Fall 2024, Fall 2025 \\Concert Orchestra - Fall 2024 \\Symphonic Winds Concert Band Ensemble – Spring 2025, Fall 2025}

        \resumeSubItem{Student Government (Spring 2025, Spring 2026)}
        {\\Regularly volunteers with senate and student government outreach to engage the student body. \\Develops senate initiatives and assists others in the academic affairs committee to do the same. \\Coauthored initiative regarding the use of Grammarly as generative AI. Currently exploring an initiative for renewable food containers in the dining hall to reduce unnecessary environmental waste. }


    \resumeSubHeadingListEnd
  

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Computational}{: Python and C++; experience with methods in HPC and bash scripting; NWCHEM and GROMACS; Phylogenetic methods (NCBI Blast, MAFFT, IQ-Tree)
}
    }
    \item{
     \textbf{Analytical}{: LC-MS/MS; IR Spectroscopy}
}
    \item{
     \textbf{Languages}{: Speak, read, and write Persian; read Avestan; knowledgeable of Gujarati
}
    }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
